---
title: "TimeSeriesBestBuy"
output:
  pdf_document: default
  html_document: default
author: "RamaKrishna"
date: "22/12/2020"
fig_width: 15
fig_height: 10
---

```{r}

InputFilePath = "E:/GIT_SBUInsights/COE/BestBuy/Data/DataScienceAssignment.xlsx"
TestForecastUnits = 16
DMNumberOfLags = 8
BufferInventory = 0.3
MinimumOrderQuantity = 50

```

## Introduction

This document covers the exploratory analysis done on the bestbuy data. Below are the key important steps to understand the data better
1. Understand the business objective
2. Load the Data and understand basic characteristics of data
3. Understand each column in the data like frequency distribution, classes in the column
4. Take a set of parameters and subset the data to run through the analysis
5. Get the general trend of the data and also the linear regression line of the data
6. Check the Stationarity of the data and if it fails use appropriate methods to stationarize ( Duck Fuller test)
7. Check the auto correlation in the data
8. Once data is correct apply time series models and validate models to understand which algorithm works well for the data
9. Plot the results 

## Loading data and understanding its basic composition.
We are loading the data from the device. And then we are tyring to look at unique combinations, which are the combination in which data is being utilised in the reports( exmaple: weekly, daily, yearly for a consumer/commercial) by the business. 

Functions to validate the existing data

```{r}
plotForecastErrors <- function(forecasterrors){
  # make a histogram of the forecast errors:
  mybinsize <- IQR(forecasterrors)/4
  mysd   <- sd(forecasterrors)
  mymin  <- min(forecasterrors) - mysd*5
  mymax  <- max(forecasterrors) + mysd*3
  # generate normally distributed data with mean 0 and standard deviation mysd
  mynorm <- rnorm(10000, mean=0, sd=mysd)
  mymin2 <- min(mynorm)
  mymax2 <- max(mynorm)
  if (mymin2 < mymin) { mymin <- mymin2 }
  if (mymax2 > mymax) { mymax <- mymax2 }
  # make a red histogram of the forecast errors, with the normally distributed data overlaid:
  mybins <- seq(mymin, mymax, mybinsize)
  hist(forecasterrors, col="red", freq=FALSE, breaks=mybins)
  # freq=FALSE ensures the area under the histogram = 1
  # generate normally distributed data with mean 0 and standard deviation mysd
  myhist <- hist(mynorm, plot=FALSE, breaks=mybins)
  # plot the normal curve as a blue line on top of the histogram of forecast errors:
  points(myhist$mids, myhist$density, type="l", col="blue", lwd=2)
}


```

First we will load the libraries in to the R Environment.

```{r}

library(pastecs, quietly = TRUE, warn.conflicts = FALSE)
library(httr, quietly = TRUE, warn.conflicts = FALSE)
library(datasets, quietly = TRUE, warn.conflicts = FALSE)
library(forecast, quietly = TRUE, warn.conflicts = FALSE)
library(stats, quietly = TRUE, warn.conflicts = FALSE)
library(openxlsx, quietly = TRUE, warn.conflicts = FALSE)
#library(xlsx, quietly = TRUE, warn.conflicts = FALSE)
library(Hmisc, quietly = TRUE, warn.conflicts = FALSE)
library(DT, quietly = TRUE, warn.conflicts = FALSE)
library(data.table, quietly = TRUE, warn.conflicts = FALSE)
library(zoo, quietly = TRUE, warn.conflicts = FALSE)
#library(rCharts, quietly = TRUE, warn.conflicts = FALSE)
library(reshape2, quietly = TRUE, warn.conflicts = FALSE)
library(ggplot2, quietly = TRUE, warn.conflicts = FALSE)
library(nnet, quietly = TRUE, warn.conflicts = FALSE)
library(tseries, quietly = TRUE, warn.conflicts = FALSE)
library(astsa, quietly = TRUE, warn.conflicts = FALSE)
library(xgboost, quietly = TRUE, warn.conflicts = FALSE)
library(keras, quietly = TRUE, warn.conflicts = FALSE)
library(tensorflow, quietly = TRUE, warn.conflicts = FALSE)
dirpath = "E:/Git_SBUInsights/COE/BestBuy/Output/ProductA/"
```

#Load the  weekly data and look at its structure


``` {R}

#read the Dataset sheet into “R”. The dataset will be called "data".

rawdata <- read.xlsx(InputFilePath)
colnames(rawdata) = c('Date', 'Product', 'Orders', 'Brand','Views', 'Cart_Adds', 'Price', 'Inventory')
rawdata$Date = as.Date(as.character(rawdata$Date), format = "%m/%d/%Y")
paste0("Duration of the Data is from  ",min(rawdata$Date), " to ",max(rawdata$Date))
str(rawdata)
```


## Adding external impact variables

```{R}
rawdata$BlackFridayWeeks = 0
rawdata$BlackFridayWeeks[(rawdata$Date>=as.Date("11/16/2020", format = "%m/%d/%Y")) & (rawdata$Date <= as.Date("12/1/2020", format = "%m/%d/%Y") )] = 1

rawdata$WinterSeason = 0
rawdata$WinterSeason[rawdata$Date>=as.Date("01/01/2020", format = "%m/%d/%Y") & rawdata$Date <= as.Date("03/15/2020", format = "%m/%d/%Y") ] = 1

rawdata$HolidayWeek = 0
rawdata$HolidayWeek[rawdata$Date>=as.Date("12/22/2019", format = "%m/%d/%Y") & rawdata$Date <= as.Date("12/29/2019", format = "%m/%d/%Y") ] = 1

rawdata$BackToSchool = 0
rawdata$BackToSchool[rawdata$Date>=as.Date("08/16/2020", format = "%m/%d/%Y") & rawdata$Date <= as.Date("09/27/2020", format = "%m/%d/%Y") ] = 1

rawdata$Spring = 0
rawdata$Spring[rawdata$Date>=as.Date("04/05/2020", format = "%m/%d/%Y") & rawdata$Date <= as.Date("05/17/2020", format = "%m/%d/%Y") ] = 1


```

## Unique Combinations of the data aand also convert the Date variable to R Date format

```{R}


dataA = rawdata[rawdata$Product=="A",]




```

```{R echo = FALSE}
getStats = function(column1,column2){
  if( length(column1) == length(column2)){
    diff = abs(column1 - column2)
    return(print(stat.desc(diff)))
  }
  else{
    return(print("Length of the two columns are not equal"))
  }
  
}

print("Descriptive Stats on different products \n\n\n")
stat.desc(dataA$Orders)
stat.desc(dataB$Orders)
stat.desc(dataC$Orders)
stat.desc(dataD$Orders)
stat.desc(dataE$Orders)


print("Descriptive Stats to identify the closeness of products \n\n\n")
# getStats(dataA$Orders,dataB$Orders)
# getStats(dataA$Orders,dataC$Orders)
# getStats(dataA$Orders,dataD$Orders)
# getStats(dataB$Orders,dataC$Orders)
# getStats(dataB$Orders,dataD$Orders)
# getStats(dataC$Orders,dataD$Orders)
```

## Trend line for the data


```{R}

trendPlot = function(data,x = "Date",y = "Orders",TrendTitle,plotfilename){
  
    filePath = paste(dirpath,plotfilename,".png",sep="")
    # Area plot
    plot = ggplot(data, aes(x = eval(parse(text=x)), y = eval(parse(text=y)))) + 
      geom_line(alpha = 0.8, position = position_dodge(0.8),colour= "green",size = 1) +
      ggtitle(TrendTitle)+xlab(x) + ylab(y) + theme(legend.title =element_blank())+
      ggsave(filePath,plot = last_plot(), dpi = 600,limitsize = TRUE,height = 7 , width = 7 * 1.5)
      return(print(plot))
}


  
trendPlot(dataA,x = "Date",y = "Orders" ,paste("Trend Line for Product_A"),"Product_A")
trendPlot(dataB,x = "Date",y = "Orders" ,paste("Trend Line for Product_B"),"Product_B")
trendPlot(dataC,x = "Date",y = "Orders" ,paste("Trend Line for Product_C"),"Product_C")
trendPlot(dataD,x = "Date",y = "Orders" ,paste("Trend Line for Product_D"),"Product_D")
trendPlot(dataE,x = "Date",y = "Orders" ,paste("Trend Line for Product_E"),"Product_E")

```

# Price factoring

```{r}
temp = dataA
temp$OrdersToViews = round(temp$Orders/(temp$Views+1),2)
table(temp$OrdersToViews,temp$Price)

```



## Displaying the linear regresion line

```{R}
# library(imputeTS)

dataA$Orders[dataA$Orders==0] = NA
x = ts(dataA$Orders,start = as.Date(min(dataA$Date)),frequency = 7)
x_interp = na.interp(x)
dataA$ActualOrders <- dataA$Orders
dataA$Orders = as.numeric(x_interp)


plot(decompose(x_interp))

Box.test(x_interp, lag=8, type="Ljung-Box") # Non Stationary

adf.test(x_interp)

kpss.test(x_interp, null="Trend")


plot(acf(x))
plot(pacf(x))



# x1 = tsclean(x)
# ## IMPUTING ##
# temp <- na.interp(x)
# temp1 <- na.StructTS(x)
# temp2 <- na.locf(x)
# temp3 <- na_interpolation(x, option = "linear")
# temp4 <- na_interpolation(x, option = "spline")
# temp5 <- na_interpolation(x, option = "stine")


# matplot(cbind(x,x1),type="l",)
# matplot(cbind(temp,x1),type="l",show.legend=FALSE)
# matplot(cbind(x,x1,temp,temp1,temp2),type="l",show.legend=FALSE)
# matplot(cbind(temp3,temp4,temp5),type="l",show.legend=FALSE)

matplot(cbind(x,x_interp),type = "l")

dataA$N_Views = (dataA$Views-mean(dataA$Views,na.rm = T))/sd(dataA$Views,na.rm = T)
dataA$N_Orders = (dataA$Orders-mean(dataA$Orders,na.rm = T))/sd(dataA$Orders,na.rm = T)
dataA$N_Cart_Adds = (dataA$Cart_Adds-mean(dataA$Cart_Adds,na.rm = T))/sd(dataA$Cart_Adds,na.rm = T)

filePath <- paste(dirpath,'AllTrends.png',sep='')
plot = ggplot(dataA, aes(x = Date)) + 
  geom_line(size=1,aes(y = N_Views,color = 'Views'), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = N_Orders,color = 'Orders'), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = N_Cart_Adds,color = 'Cart_Adds'), position = position_dodge(0.8)) +
  ggtitle(paste('Trends of Views, Cart_Adds & Orders ( Normalised) ', collapse = '\n'))+
  theme(plot.title = element_text(size = 16, face = 'bold',hjust = 0.5))+
  ggsave(filePath,plot = last_plot(), dpi = 600,limitsize = TRUE,height = 10 , width = 10 * 1.5)

print(plot)


```

```{r}
tempdata = dataA[,c("Date","Orders","BlackFridayWeeks","WinterSeason","HolidayWeek","BackToSchool","Spring")]

tempdata$Orders <- as.numeric(ts(tempdata$Orders,start = as.Date(min(tempdata$Date)),frequency = 7))
tempdata$Orders <- round(tempdata$Orders,0)
tempdata$Type = "Actual"


testData=data.frame(Date= seq(max(tempdata$Date)+7, max(tempdata$Date)+(7*TestForecastUnits), by="week"))
testData$Orders = 0
testData$Date = as.Date(testData$Date)
testData$Type = "Forecast"

testData$BlackFridayWeeks = 0
testData$BlackFridayWeeks[testData$Date>=as.Date("11/22/2021", format = "%m/%d/%Y") & testData$Date <= as.Date("12/1/2021", format = "%m/%d/%Y") ] = 1

testData$WinterSeason = 0
testData$WinterSeason[testData$Date>=as.Date("01/01/2021", format = "%m/%d/%Y") & testData$Date <= as.Date("03/01/2021", format = "%m/%d/%Y") ] = 1

testData$HolidayWeek = 0
testData$HolidayWeek[testData$Date>=as.Date("12/20/2020", format = "%m/%d/%Y") & testData$Date <= as.Date("12/27/2020", format = "%m/%d/%Y") ] = 1

testData$BackToSchool = 0
testData$BackToSchool[testData$Date>=as.Date("08/15/2021", format = "%m/%d/%Y") & testData$Date <= as.Date("09/26/2021", format = "%m/%d/%Y") ] = 1

testData$Spring= 0
testData$Spring[testData$Date>=as.Date("04/04/2021", format = "%m/%d/%Y") & testData$Date <= as.Date("05/16/2021", format = "%m/%d/%Y") ] = 1

totaldata = rbind(tempdata,testData)
totaldata[is.na(totaldata)] <- 0

```



```{r}

fitreg  <- auto.arima(x,xreg = as.matrix(totaldata[totaldata$Type=="Actual",c("BlackFridayWeeks","WinterSeason","HolidayWeek","BackToSchool","Spring")]),trace=TRUE)
summary(fitreg)
predict_dataMREGArima = predict(fitreg, newxreg = as.matrix(totaldata[totaldata$Type=="Forecast",c("BlackFridayWeeks","WinterSeason","HolidayWeek","BackToSchool","Spring")]))


totaldata$Orders[totaldata$Type=="Forecast"] = predict_dataMREGArima$pred
filePath = paste(dirpath,"MREGArima.png",sep="")

# Area plot
plot = ggplot(totaldata, aes(x = Date, y = Orders)) + 
  geom_line(aes(color = Type), 
            alpha = 1, position = position_dodge(0.8)) +
  ggtitle(paste(" MultiVariant Arima - Trend and Forecast Line for Product A ",sep=""))+
 # scale_color_manual(Orderss = c("#00AFBB", "#E7B800")) +
 # scale_fill_manual(Orderss = c("#00AFBB", "#E7B800")) +
  ggsave(filePath,plot = last_plot(), dpi = 600,limitsize = TRUE,height = 7 , width = 7 * 1.5)
print(plot)


forecasttrendPlot = function(data,x = "Date",y = "Orders",TrendTitle ="Line Chart",plotfilename = "Chart",bycolor = "Type"){
  
    filePath = paste(dirpath,plotfilename,".png",sep="")
    # Area plot
    plot = ggplot(data, aes(x = eval(parse(text=x)), y = eval(parse(text=y)))) + 
      geom_line(aes(color =  eval(parse(text=bycolor))),
                alpha = 0.8, position = position_dodge(0.8),size = 1) +
      ggtitle(TrendTitle)+xlab(x) + ylab(y) + theme(legend.title =element_blank())+
      ggsave(filePath,plot = last_plot(), dpi = 600,limitsize = TRUE,height = 7 , width = 7 * 1.5)
      return(print(plot))
}

forecasttrendPlot(totaldata,x = "Date",y = "Orders",TrendTitle =paste(" MultiVariant Arima - Trend and Forecast Line for Product A ",sep=""),plotfilename = "MREGArima.png",bycolor = "Type")

totaldata$MAutoArima <- totaldata$Orders

```


```{r}
HoltMod = HoltWinters(ts(totaldata$Orders[totaldata$Type =="Actual"]),beta = TRUE,gamma = FALSE)
plot(HoltMod)
HoltModforecasts <- predict(HoltMod,  n.ahead = TestForecastUnits)

totaldata$Orders[totaldata$Type=="Forecast"] = HoltModforecasts


forecasttrendPlot(totaldata,x = "Date",y = "Orders",TrendTitle =paste(" Holts - Trend and Forecast Line for Product A ",sep=""),plotfilename = "Holts.png",bycolor = "Type")

plot(HoltMod,HoltModforecasts)

totaldata$HoltWinters <- totaldata$Orders

```

##  ETS ( Smoothing Techniques) Forecast
```{r}



etsreg = ets(totaldata$Orders[totaldata$Type =="Actual"],model = "ZZZ",damped = NULL,lambda = "auto")
predict_dataETS <- as.data.frame(forecast(etsreg,TestForecastUnits))
totaldata$Orders[totaldata$Type=="Forecast"] = predict_dataETS$`Point Forecast`

forecasttrendPlot(totaldata,x = "Date",y = "Orders",TrendTitle =paste("ETS - Trend and Forecast Line for dataA ",sep=""),plotfilename = "ETS.png",bycolor = "Type")
totaldata$ETS <- totaldata$Orders

```
## Neural Net FOrecast
```{r}
#Non Linear Patterns

nnetdata = totaldata$Orders[totaldata$Type=="Actual"] + 1
#nnetdata = log(nnetdata)
fitreg = nnetar(nnetdata)
predict_datannet <- as.data.frame(forecast(fitreg,TestForecastUnits))
#predict_datannet$`Point Forecast` <- exp(predict_datannet$`Point Forecast`)
totaldata$Orders[totaldata$Type=="Forecast"] = predict_datannet$`Point Forecast`

forecasttrendPlot(totaldata,x = "Date",y = "Orders",TrendTitle =paste("Neural Net - Trend and Forecast Line for Series for product A ",sep=""),plotfilename = "NNET.png",bycolor = "Type")

totaldata$NNET <- totaldata$Orders
```
## Using External Variables

```{r}
totaldata1 = totaldata[,c("Date","Type","Orders","BlackFridayWeeks","WinterSeason","HolidayWeek","BackToSchool","Spring")]
```


## XGBoost

```{r}
xgtotaldata <- totaldata1
xgtotaldata$Orders[xgtotaldata$Type == "Forecast"] = 0
xgtotaldata$WeekDay <- as.POSIXlt(as.Date(xgtotaldata$Date))$wday
xgtotaldata$MDay <- mday(as.Date(xgtotaldata$Date))
xgtotaldata$Month = month(xgtotaldata$Date)
AvgxgtotaldataOrders = mean(xgtotaldata$Orders[xgtotaldata$Type=="Actual"])
xgtotaldata$Orders = xgtotaldata$Orders-AvgxgtotaldataOrders
#xgtotaldata$Year  = year(xgtotaldata$Date)
training_data = xgtotaldata[xgtotaldata$Type=="Actual",]
test_data = xgtotaldata[xgtotaldata$Type=="Forecast",]
  
# Split data training and test data into X and Y
  X_train = data.matrix(training_data[,c("BlackFridayWeeks","WinterSeason" ,"HolidayWeek","BackToSchool","Spring" ,"WeekDay","MDay" ,"Month")])
  Y_train = data.matrix(training_data[,"Orders"])
  class(X_train)[1]
  class(Y_train)
  
  X_test = data.matrix(test_data[,c("BlackFridayWeeks","WinterSeason" ,"HolidayWeek","BackToSchool","Spring" ,"WeekDay","MDay" ,"Month")])
  Y_test = data.matrix(test_data[,"Orders"])
  class(X_test)[1]
  class(Y_test)
  
  
  # Train the xgboost model using the "xgboost" function
  dtrain = xgb.DMatrix(data = X_train, label = Y_train)
  xgModel = xgboost(data = dtrain, nround = 16, booster="gblinear",eta = 0.02, objective = "reg:squarederror",eval_metric  = "rmse")
  
  # Make the predictions on the test data
  predict_data = predict(xgModel, X_test)

  xgtotaldata$Orders[xgtotaldata$Type == "Forecast"] = predict_data
  xgtotaldata$Orders = xgtotaldata$Orders+AvgxgtotaldataOrders


forecasttrendPlot(totaldata,x = "Date",y = "Orders",TrendTitle =paste(" XGBoost - Trend and Forecast Line for ProductA",sep=""),plotfilename = "XGBoost.png",bycolor = "Type")


totaldata$XGBoost <- xgtotaldata$Orders

```
# Prophet Model

```{r}
library(prophet)
library(dplyr)
BlackFridayWeeks <- data_frame(
  holiday = 'BlackFriday',
  ds = c(seq(as.Date("11/22/2020", format = "%m/%d/%Y"), as.Date("12/06/2020", format = "%m/%d/%Y"),by="week"), seq(as.Date("11/19/2021", format = "%m/%d/%Y"), as.Date("12/03/2021", format = "%m/%d/%Y"),by="week")),
  lower_window = 0,
  upper_window = 2
)
WinterSeason <- data_frame(
  holiday = 'WinterSeason',
  ds = c(seq(as.Date("01/01/2020", format = "%m/%d/%Y"), as.Date("03/01/2020", format = "%m/%d/%Y"),by="week"), seq(as.Date("01/01/2021", format = "%m/%d/%Y"), as.Date("03/01/2021", format = "%m/%d/%Y"),by="week")),
  lower_window = 0,
  upper_window = 1
)

HolidayWeek <- data_frame(
  holiday = 'HolidayWeek',
  ds = c(seq(as.Date("12/22/2019", format = "%m/%d/%Y"), as.Date("12/29/2019", format = "%m/%d/%Y"),by="week"), seq(as.Date("12/20/2020", format = "%m/%d/%Y"), as.Date("12/27/2020", format = "%m/%d/%Y"),by="week")),
  lower_window = 0,
  upper_window = 1
)

BackToSchool <- data_frame(
  holiday = 'BackToSchool',
  ds = c(seq(as.Date("08/15/2021", format = "%m/%d/%Y"), as.Date("09/26/2021", format = "%m/%d/%Y"),by="week"), seq(as.Date("08/16/2020", format = "%m/%d/%Y"), as.Date("09/27/2020", format = "%m/%d/%Y"),by="week")),
  lower_window = 0,
  upper_window = 1
)

Spring <- data_frame(
  holiday = 'Spring',
  ds = c(seq(as.Date("04/04/2021", format = "%m/%d/%Y"), as.Date("05/16/2021", format = "%m/%d/%Y"),by="week"), seq(as.Date("04/05/2020", format = "%m/%d/%Y"), as.Date("05/17/2020", format = "%m/%d/%Y"),by="week")),
  lower_window = 0,
  upper_window = 1
)


holidays <- bind_rows(BlackFridayWeeks, WinterSeason,HolidayWeek,BackToSchool,Spring)


tempdata1 = totaldata[totaldata$Type =="Actual",c("Date","Orders")]
colnames(tempdata1) = c("ds","y")
totaldata$Prophet = totaldata$Orders

future <- data.frame(ds= seq(min(tempdata$Date), max(tempdata$Date)+(7*TestForecastUnits), by="week"))
m <- prophet(holidays = holidays)
m <- add_country_holidays(m, country_name = 'CA')
m <- fit.prophet(m, tempdata1)
forecast <- predict(m, future)
totaldata$Prophet[totaldata$Type=="Forecast"]= forecast$yhat
plot(m,forecast)
prophet_plot_components(m,forecast)
forecasttrendPlot(totaldata,x = "Date",y = "Orders",TrendTitle =paste(" PROPHET - Trend and Forecast Line for ProductA",sep=""),plotfilename = "Prophet.png",bycolor = "Type")



```


```{r}


DMNumberOfLags = 8

#totaldata$WeekDay <- as.POSIXlt(as.Date(totaldata$Date))$wday
totaldata$MDay <- mday(as.Date(totaldata$Date))
totaldata$Month = month(totaldata$Date)

totaldata$Month = as.factor(totaldata$Month)
#totaldata$WeekDay = as.factor(totaldata$WeekDay)
totaldata$MDay = as.factor(totaldata$MDay)

for(i in 1:DMNumberOfLags) {
  #print(i)
  totaldata[,paste("Lag_",i,sep="")] = Lag(totaldata$Orders,i)
} 

totaldata[is.na(totaldata)] <- 0

totaldata$glmnetOrders <- totaldata$Orders
totaldata$glmnet.poisOrders <- totaldata$Orders
totaldata$lmOrders <- totaldata$Orders
totaldata$earthOrders <- totaldata$Orders
totaldata$earth.poisOrders <- totaldata$Orders
totaldata$gbmOrders <- totaldata$Orders
totaldata$gamOrders <- totaldata$Orders
totaldata$rfOrders <- totaldata$Orders
totaldata$rpartOrders <- totaldata$Orders
totaldata$partyOrders <- totaldata$Orders

totaldata <- totaldata[order(totaldata$Date,decreasing = FALSE),]
rownames(totaldata) <-NULL

#totaldata <- totaldata[DMNumberOfLags+1 : nrow(totaldata),]


DMcovariates <- c("BlackFridayWeeks","WinterSeason" ,"HolidayWeek","BackToSchool","Spring","Month","MDay","Lag_1","Lag_2","Lag_3","Lag_4","Lag_5","Lag_6","Lag_7","Lag_8")

#### creating sampling seeds ####
set.seed(123)
seeds <- vector(mode = "list", length = (nrow(totaldata)+100))
for(i in 1:(nrow(totaldata)+100-1)) seeds[[i]] <- sample.int(1000, 5)

## For the last model:
seeds[[(nrow(totaldata)+100)]] <- sample.int(1000, 1)

library(caret)

myTimeControl <- trainControl(method = "timeslice",
                              initialWindow = 20,
                              horizon = 4,
                              fixedWindow = FALSE,
                              allowParallel = TRUE,
                              seeds = seeds)

tuneLength.num <- 5

```


```{r}
# trainData = totaldata[totaldata$Type == "Actual",]
# testData = totaldata[totaldata$Type == "Forecast",]

library(glmnet)

glmnet.mod <- train(glmnetOrders ~ BlackFridayWeeks+WinterSeason+HolidayWeek+BackToSchool+Spring+Month+MDay+Lag_1+Lag_2+Lag_3+Lag_4+Lag_5+Lag_6+Lag_7+Lag_8,
                    data = totaldata[totaldata$Type == "Actual",],
                    method = "glmnet",
                    family = "gaussian",
                    trControl = myTimeControl,
                    tuneLength=tuneLength.num)

```


```{r}
# glmnetPredictions = predict(glmnet.mod,testData )
# totaldata$glmnetOrders[totaldata$Type == "Forecast"] <- glmnetPredictions
library(glmnet)
pois.mod <- train(glmnet.poisOrders ~ BlackFridayWeeks+WinterSeason+HolidayWeek+BackToSchool+Spring+Month+MDay+Lag_1+Lag_2+Lag_3+Lag_4+Lag_5+Lag_6+Lag_7+Lag_8,
                  data = totaldata[totaldata$Type == "Actual",],
                  method = "glmnet",
                  family = "poisson",
                  trControl = myTimeControl,
                  tuneLength=tuneLength.num)

#glmnet.poisPredictions = predict(pois.mod,testData )
# totaldata$glmnet.poisOrders[totaldata$Type == "Forecast"] <- glmnet.poisPredictions
```

```{r}
earth.mod <- train(earthOrders ~ BlackFridayWeeks+WinterSeason+HolidayWeek+BackToSchool+Spring+Month+MDay+Lag_1+Lag_2+Lag_3+Lag_4+Lag_5+Lag_6+Lag_7+Lag_8,
                   data = totaldata[totaldata$Type == "Actual",],
                   method = "earth",
                   trControl = myTimeControl,
                   tuneLength=tuneLength.num)

# earthPredictions = predict(earth.mod,testData )
# totaldata$earthOrders[totaldata$Type == "Forecast"] <- earthPredictions
```


```{r}
rpart.mod <- train(rpartOrders ~ BlackFridayWeeks+WinterSeason+HolidayWeek+Month+MDay+Lag_1+Lag_2+Lag_3+Lag_4+Lag_5+Lag_6+Lag_7+Lag_8,
                   data = totaldata[totaldata$Type == "Actual",],
                   method = "rpart",
                   trControl = myTimeControl,
                   tuneLength=tuneLength.num)

# rpartPredictions = predict(rpart.mod,testData )
# totaldata$rpartOrders[totaldata$Type == "Forecast"] <- rpartPredictions
```


```{r}
party.mod <- train(partyOrders ~ BlackFridayWeeks+WinterSeason+HolidayWeek+Month+MDay+Lag_1+Lag_2+Lag_3+Lag_4+Lag_5+Lag_6+Lag_7+Lag_8,
                   data = totaldata[totaldata$Type == "Actual",],
                   method = "ctree",
                   trControl = myTimeControl,
                   tuneLength=tuneLength.num)

# partyPredictions = predict(party.mod,testData )
# totaldata$partyOrders[totaldata$Type == "Forecast"] <- partyPredictions
```


```{r}
rf.mod <- train(rfOrders ~ BlackFridayWeeks+WinterSeason+HolidayWeek+Month+MDay+Lag_1+Lag_2+Lag_3+Lag_4+Lag_5+Lag_6+Lag_7+Lag_8,
                data = totaldata[totaldata$Type == "Actual",],
                method = "rf",
                trControl = myTimeControl,
                tuneLength=tuneLength.num)

# rfPredictions = predict(rf.mod,testData )
# totaldata$rfOrders[totaldata$Type == "Forecast"] <- rfPredictions
# 
```



```{r}

# ### model performance ###
# 
# resamps <- resamples(list(glmnet = glmnet.mod,
#                           glmnet.pois = pois.mod,
#                           lm = lm.mod,
#                           earth=earth.mod,
#                           earth.pois=earth.pois.mod,
#                           gbm=gbm.mod,
#                           gam=gam.mod,
#                           rf=rf.mod,
#                           rpart=rpart.mod,
#                           party=party.mod))
# resamps
# 
# ss <- summary(resamps)

for(i in (nrow(totaldata[totaldata$Type == "Actual",])+1):nrow(totaldata)){
  
  for(j in 1:DMNumberOfLags) {
    #print(i)
    totaldata[,paste("Lag_",j,sep="")] = Lag(totaldata$glmnetOrders,j)
  } 
  SampleX_test <- data.matrix(totaldata[i,DMcovariates])

  
  glmnetPredictions = predict(glmnet.mod,totaldata[i,DMcovariates] )
  totaldata$glmnetOrders[i] <- glmnetPredictions

  
  for(j in 1:DMNumberOfLags) {
    #print(i)
    totaldata[,paste("Lag_",j,sep="")] = Lag(totaldata$glmnet.poisOrders,j)
  } 
  
  glmnet.poisPredictions = exp(predict(pois.mod,totaldata[i,DMcovariates]))
  totaldata$glmnet.poisOrders[i] <- glmnet.poisPredictions
  
  for(j in 1:DMNumberOfLags) {
    #print(i)
    totaldata[,paste("Lag_",j,sep="")] = Lag(totaldata$earthOrders,j)
  } 
  
  earthPredictions = predict(earth.mod,totaldata[i,DMcovariates])
  totaldata$earthOrders[i] <- earthPredictions


  
  for(j in 1:DMNumberOfLags) {
    #print(i)
    totaldata[,paste("Lag_",j,sep="")] = Lag(totaldata$rpartOrders,j)
  } 
  
  rpartPredictions = predict(rpart.mod,totaldata[i,DMcovariates] )
  totaldata$rpartOrders[i] <- rpartPredictions
  
  for(j in 1:DMNumberOfLags) {
    #print(i)
    totaldata[,paste("Lag_",j,sep="")] = Lag(totaldata$partyOrders,j)
  } 
  
  partyPredictions = predict(party.mod,totaldata[i,DMcovariates] )
  totaldata$partyOrders[i] <- partyPredictions
  
  for(j in 1:DMNumberOfLags) {
    #print(i)
    totaldata[,paste("Lag_",j,sep="")] = Lag(totaldata$rfOrders,j)
  } 
  
  rfPredictions = predict(rf.mod,totaldata[i,DMcovariates] )
  totaldata$rfOrders[i] <- rfPredictions
  
}


forecasttrendPlot(totaldata,x = "Date",y = "glmnetOrders",TrendTitle =paste(" GLMNET - Trend and Forecast Line for ProductA",sep=""),plotfilename = "GLMNET.png",bycolor = "Type")
forecasttrendPlot(totaldata,x = "Date",y = "earthOrders",TrendTitle =paste(" EARTH - Trend and Forecast Line for ProductA",sep=""),plotfilename = "EARTH.png",bycolor = "Type")
forecasttrendPlot(totaldata,x = "Date",y = "rfOrders",TrendTitle =paste(" RandomForest - Trend and Forecast Line for ProductA",sep=""),plotfilename = "RandomForest.png",bycolor = "Type")
forecasttrendPlot(totaldata,x = "Date",y = "rpartOrders",TrendTitle =paste(" RPART - Trend and Forecast Line for ProductA",sep=""),plotfilename = "RPART.png",bycolor = "Type")
forecasttrendPlot(totaldata,x = "Date",y = "partyOrders",TrendTitle =paste(" PARTY - Trend and Forecast Line for ProductA",sep=""),plotfilename = "PARTY.png",bycolor = "Type")



```


```{r}
library(ggplot2)
#library(plotly)
filePath <- paste(dirpath,'All Models_Product_A.png',sep='')
plot = ggplot(totaldata, aes(x = Date)) + 
  geom_line(size=1,aes(y = glmnetOrders,color = 'glmnetOrders'), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = earthOrders,color = 'earthOrders'), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = rfOrders,color = 'rfOrders'), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = rpartOrders,color = 'rpartOrders'), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = partyOrders,color = 'partyOrders'), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = ETS,color = 'ETSOrders'), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = NNET,color = 'NNETOrders'), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = MAutoArima,color = 'MAutoArimaOrders'), position = position_dodge(0.8)) +
  #geom_line(size=1,aes(y = HoltWinters,color = 'HoltsOrders'), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = XGBoost,color = 'XGBoostOrders'), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = Prophet,color = 'Prophet'), position = position_dodge(0.8)) +
  ggtitle(paste('Forecasts from different models - Product A ', collapse = '\n'))+
  theme(plot.title = element_text(size = 12, face = 'bold',hjust = 0.5))+
  # scale_colour_manual(Values = c(glmnetOrders = '#999999', earthOrders='#E69F00', rfOrders= '#F0E442',rpartOrders= '#0072B2', partyOrders='#D55E00', ETS='#CC79A7',NNET='#CC6666', MAutoArima='#9999CC',HoltWinters= '#66CC99',XGBoost='grey',Prophet='pink')) +
  ggsave(filePath,plot = last_plot(), dpi = 600,limitsize = TRUE,height = 10 , width = 10 * 1.5)

print(plot)


```




# Ensemble of selected models
```{r}
for (i in 1:nrow(totaldata)) {
totaldata$EnsembleForecast[i] = mean(c(totaldata$MAutoArima[i],totaldata$NNET[i],totaldata$XGBoost[i],totaldata$Prophet[i],totaldata$ETS[i],totaldata$glmnetOrders[i],totaldata$partyOrders[i],totaldata$rfOrders[i],totaldata$rpartOrders[i],totaldata$earthOrders[i]),na.rm =TRUE)
}


filePath = paste(dirpath,"Ensemble.png",sep="")
# Area plot
plot = ggplot(totaldata, aes(x = Date, y = EnsembleForecast)) + 
  geom_line(aes(color = Type), 
            alpha = 1, position = position_dodge(0.8)) +
  ggtitle(paste("Ensemble- Trend and Forecast Line for Series for DataA ",sep=""))+
  # scale_color_manual(Orderss = c("#00AFBB", "#E7B800")) +
  # scale_fill_manual(Orderss = c("#00AFBB", "#E7B800")) +
  ggsave(filePath,plot = last_plot(), dpi = 600,limitsize = TRUE,height = 7 , width = 7 * 1.5)
print(plot)

```

## Optimization of Inventory
## Key Assumptions
1. Assuming

```{r}

FinalData <- totaldata[,c("Date","Type","EnsembleForecast")]
FinalData$EnsembleForecast <- round(FinalData$EnsembleForecast,0)
FinalData$Orders[FinalData$Type=="Actual"] <- round(dataA$ActualOrders,0)
FinalData$Inventory[FinalData$Type=="Actual"] <- dataA$Inventory
FinalData$Cart_Adds[FinalData$Type=="Actual"] <- dataA$Cart_Adds
FinalData$Views[FinalData$Type=="Actual"] <- dataA$Views


FinalData$Orders[FinalData$Type=="Forecast"] <- 0
FinalData$Inventory[FinalData$Type=="Forecast"] <- 0
FinalData$Cart_Adds[FinalData$Type=="Forecast"] <- 0
FinalData$Views[FinalData$Type=="Forecast"] <- 0

FinalData[is.na(FinalData)] <- 0


FinalData$Inventory_StartOfWeek[FinalData$Type=="Actual"] <- FinalData$Orders[FinalData$Type=="Actual"] + FinalData$Inventory[FinalData$Type=="Actual"]




FinalData$InventoryReplenished <-0

for(i in 1:nrow(FinalData)){
  
  if (FinalData$Type[i] =="Actual" & (i >1)){
    FinalData$InventoryReplenished[i] =  FinalData$Inventory_StartOfWeek[i]-FinalData$Inventory[i-1]
    
  }
  
  else if (FinalData$Type[i] == "Forecast"){
    
  FinalData$Orders[i] = FinalData$EnsembleForecast[i]
  #IdealInventory = mean(FinalData$EnsembleForecast[(i-4):(i-1)]) * (1+BufferInventory)
  IdealInventory = FinalData$EnsembleForecast[i] * (1+BufferInventory)
  
  if ( FinalData$Inventory[i-1] >= IdealInventory){
    FinalData$InventoryReplenished[i]=0
  }
  else if(FinalData$Inventory[i-1] < IdealInventory){
    ExtraInventoryNeeded= ( IdealInventory-FinalData$Inventory[i-1] )
    if((ExtraInventoryNeeded %% MinimumOrderQuantity) > 0.0){
      BlocksOf50<- round((ExtraInventoryNeeded%/%MinimumOrderQuantity)+1,0)
    }
    else{
    BlocksOf50<- round(ExtraInventoryNeeded%/%MinimumOrderQuantity,0)  
    }
    
    FinalData$InventoryReplenished[i] = BlocksOf50 * 50
  } 
  
  FinalData$Inventory[i] <- FinalData$InventoryReplenished[i]+FinalData$Inventory[i-1] - FinalData$Orders[i]
  
  }
}

# AverageCartAddsToOrdersRatio= mean(dataA$EnsembleForecast/dataA$Cart_Adds,na.rm = TRUE)
# AverageViewsToOrdersRatio= mean(dataA$EnsembleForecast/dataA$Views,na.rm = TRUE)
# 
# print(AverageCartAddsToOrdersRatio)
# print(AverageViewsToOrdersRatio)
filePath <- paste(dirpath, 'OF&IS.png',sep='')
plot = ggplot(FinalData, aes(x = Date)) + 
  geom_line(size=1,aes(y = Orders,color = "Orders"), position = position_dodge(0.8)) +
  geom_line(size=1,aes(y = InventoryReplenished,color = "InventoryReplenished"), position = position_dodge(0.8)) +
  geom_vline(xintercept=as.numeric(max(FinalData$Date[FinalData$Type=="Actual"])), linetype=4)+
  ggtitle(paste("Orders Forecast & Inventory Schedule", collapse = '\n'))+
  theme(plot.title = element_text(size = 12, face = 'bold',hjust = 0.5))+
  ggsave(filePath,plot = last_plot(), dpi = 600,limitsize = TRUE,height = 10 , width = 10 * 1.5)

print(plot)

```


```{r}
write.csv(FinalData, paste(dirpath,"Product_A.csv",sep=""), row.names=FALSE)
```